Supplementary Materials

### 2018-03-27 paper/application.tex
update task

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
In this section, we discuss application scenarios, in which the domain experts utilize the perturbation driven analysis to explore and assess the model and interpret the attention mechanism.
These scenarios are summarized by the domain experts who try to integrate the tool into their workflow.

\subsection{Scenario 1: Interpreting Decision Making Process}
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
Mistake can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

\subsection{Scenario 2: Assess the Model Prediction Stability}
Utilize input sentence perturbation to assess the overall stability of the prediction

\subsection{Scenario 3: What Does It Take to Correct the Prediction?}
In the previous section, we discussed how we can use forward prediction

@@

\subsection{Scenario 5: Grammar Structure and Attention}
Can attention capture grammar structure? Is 
%\subsection{Is the Prediction Stable?}
%\subsection{Where Are the Mistakes?}
%\subsection{How Attention Affect the Prediction?}
%\subsection{What Does It Take to Change the Prediction?}
%\subsection{Is Attention All You Need?}

>>>>

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the 
To illustrate how the proposed perturbation-driven exploration tool help the domain experts interpret the neural network model,
summarized  and interpret the attention mechanism.
These scenarios are summarized by the domain experts who integrating the proposed tool into their model analysis workflow.

\subsection{Scenario 1: Interpreting Decision Making Process}
Understanding the decision making process, i.e., why the model make a prediction, is most crucial aspect in model analysis.
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

\subsection{Scenario 2: What Does It Take to Correct a Wrong Prediction?}
In the previous section, we discussed how we can use forward prediction

\subsection{Scenario 3: Assess the Model Prediction Stability}
Utilize input sentence perturbation to assess the overall stability of the prediction

@@

\subsection{Scenario 5: Explore Relationship Between Grammar and Attention}
Can attention capture grammar structure? Is 
%\subsection{Is the Prediction Stable?}
%\subsection{Where Are the Mistakes?}
%\subsection{How Attention Affect the Prediction?}
%\subsection{What Does It Take to Change the Prediction?}
%\subsection{Is Attention All You Need?}

### 2018-03-27 paper/task.tex
update task

    \item So far, we focus on how changes in earlier stage of the model affect later stages or final prediction. However, what if the current prediction is wrong, how can we apply minimal update to the model to produce correct prediction and how would such a modification affect attention.
    Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).
\end{itemize}
%
% Based on the NLP analysis goals, we identify the visualization tasks to achieve these goals.

>>>>

    \item So far, we have focused on how changes in earlier stage of the model affect later stages or the final prediction. However, what if the current prediction is wrong, where and how can we apply update to the model to produce correct prediction and how the attention respond to such a change (\textbf{T3}).
    %Therefore, thirdly, we want to explore how model should be updated to produce the desirable change of prediction, and how the attention respond to such a change (\textbf{T3}).
\end{itemize}
%
% Based on the NLP analysis goals, we identify the visualization tasks to achieve these goals.
